Example of a simple compiler pass for each problem, which makes that problem obvious

Big passes:
* null as default and absent
* inter-dependency between pieces of code which generate certain information
  * list of methods for a class vs. list of classes on which a method is present

Graph manipulation:
* fail to update a reference to an updated element
  * specialize a method on its receiver type: object or primitive. Update method calls, dispatch for boxed primitives, but forget to update method pointer creation
  * update methods: indicate whether their receiver can be a primitive type. Update calls to point to the new version, but forget to update the list of methods on the class. Or more devious: update the list of methods, but forget to make the method's ``declaringClass'' field point to the updated class.
* or issues with identity (e.g. Mono.Cecil bug)
* lookup of a key which does not exist anymore, because the node was deleted in the meantime.
  * remove methods which are dead code, but fail to delete some reference to that name in a list of method names.

Unit tests:
* Write a test for an instruction transformation (unary negation to binary subtraction), show that it requires a class, method, main method etc.

Graph construction:
* languages with mutation: 
* purely functional language: promises have to be forced, or explicit lookups
* argue that purely functional languages make GC easy to design, parallelize more easily, type system easier to design and more flexible (monomorphism restriction), but lazy languages are harder to debug.

Generic graph algorithms
* depth-first search, aggregates information from nodes of two different types: show how you have to re-write it if your data structure changes a bit
* or SCC (has_cycles), where some links matter but some don't

Structural constraints
* compute the in-memory size of a C structure: should not have any cycles
* off-by-one when updating the number of references to an element
* PHOAS



Downsides
* $\alpha$-renaming: problematic, since there is no declaration / use of fields anymore.
=> IDE solution: keep track of which pass introduces which field.